---
title: "multi_year_cleaning"
author: "Ethan Tenison"
date: "10/10/2020"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(readr)
library(readxl)
```

**Merging Dataframes**

```{r message=FALSE, warning=FALSE}

df1 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Spring 2016, C1-2.xlsx"
  )
df2 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Spring 2016, C3-4.xlsx"
  )
varList <-
  names(df2)[!(names(df2) %in% names(df1))] # get non common names
varList <- c(varList, "EID") # appending key parameter
spring2016 <-
  df1 %>% left_join((df2 %>% select(varList)), by = "EID") %>% mutate(semester = "Spring 2016")
names(spring2016)[4] <- "Academic Status"
names(spring2016)[24] <- "Semester GPA Hrs w/o CBE"
names(spring2016)[30] <- "Prob-Dism, Begin of semester"
names(spring2016)[31] <- "Prob-Dism, Most Recent"
names(spring2016)[69] <- "Semester GPA"
names(spring2016)[71] <- "Semester Hrs Failed"
names(spring2016)[72] <- "Semester Hrs Incomplete"
#29 and 70 have redundant information
spring2016 <- spring2016[-c(29, 70)]

df1 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Fall 2016, C1-2.xlsx"
  )
df2 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Fall 2016, C3-4.xlsx"
  )
varList <-
  names(df2)[!(names(df2) %in% names(df1))] # get non common names
varList <- c(varList, "EID") # appending key parameter
fall2016 <-
  df1 %>% left_join((df2 %>% select(varList)), by = "EID") %>% mutate(semester = "Fall 2016")
names(fall2016)[4] <- "Academic Status"
names(fall2016)[24] <- "Semester GPA Hrs w/o CBE"
names(fall2016)[30] <- "Prob-Dism, Begin of semester"
names(fall2016)[31] <- "Prob-Dism, Most Recent"
names(fall2016)[69] <- "Semester GPA"
names(fall2016)[71] <- "Semester Hrs Failed"
names(fall2016)[72] <- "Semester Hrs Incomplete"
#29 and 70 have redundant information
fall2016 <- fall2016[-c(29, 70)]

df1 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Spring 2017, C1-2.xlsx"
  )
df2 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Spring 2017, C3-4.xlsx"
  )
varList <-
  names(df2)[!(names(df2) %in% names(df1))] # get non common names
varList <- c(varList, "EID") # appending key parameter
spring2017 <-
  df1 %>% left_join((df2 %>% select(varList)), by = "EID") %>% mutate(semester = "Spring 2017")
names(spring2017)[4] <- "Academic Status"
names(spring2017)[24] <- "Semester GPA Hrs w/o CBE"
names(spring2017)[30] <- "Prob-Dism, Begin of semester"
names(spring2017)[31] <- "Prob-Dism, Most Recent"
names(spring2017)[69] <- "Semester GPA"
names(spring2017)[71] <- "Semester Hrs Failed"
names(spring2017)[72] <- "Semester Hrs Incomplete"
spring2017 <- spring2017[-c(29, 70)]

df1 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Fall 2017, C1-2.xlsx"
  )
df2 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Fall 2017, C3-4.xlsx"
  )
varList <-
  names(df2)[!(names(df2) %in% names(df1))] # get non common names
varList <- c(varList, "EID") # appending key parameter
fall2017 <-
  df1 %>% left_join((df2 %>% select(varList)), by = "EID") %>% mutate(semester = "Fall 2017")
names(fall2017)[4] <- "Academic Status"
names(fall2017)[24] <- "Semester GPA Hrs w/o CBE"
names(fall2017)[30] <- "Prob-Dism, Begin of semester"
names(fall2017)[31] <- "Prob-Dism, Most Recent"
names(fall2017)[69] <- "Semester GPA"
names(fall2017)[71] <- "Semester Hrs Failed"
names(fall2017)[72] <- "Semester Hrs Incomplete"
fall2017 <- fall2017[-c(29, 70)]

df1 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Spring 2018, C1-2.xlsx"
  )
df2 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Spring 2018, C3-4.xlsx"
  )
varList <-
  names(df2)[!(names(df2) %in% names(df1))] # get non common names
varList <- c(varList, "EID") # appending key parameter
spring2018 <-
  df1 %>% left_join((df2 %>% select(varList)), by = "EID") %>% mutate(semester = "Spring 2018")
names(spring2018)[4] <- "Academic Status"
names(spring2018)[24] <- "Semester GPA Hrs w/o CBE"
names(spring2018)[30] <- "Prob-Dism, Begin of semester"
names(spring2018)[31] <- "Prob-Dism, Most Recent"
names(spring2018)[69] <- "Semester GPA"
names(spring2018)[71] <- "Semester Hrs Failed"
names(spring2018)[72] <- "Semester Hrs Incomplete"
spring2018 <- spring2018[-c(29, 70)]

df1 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Fall 2018, C1-2.xlsx"
  )
df2 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Fall 2018, C3-4.xlsx"
  )
varList <-
  names(df2)[!(names(df2) %in% names(df1))] # get non common names
varList <- c(varList, "EID") # appending key parameter
fall2018 <-
  df1 %>% left_join((df2 %>% select(varList)), by = "EID") %>% mutate(semester = "Fall 2018")
names(fall2018)[4] <- "Academic Status"
names(fall2018)[24] <- "Semester GPA Hrs w/o CBE"
names(fall2018)[30] <- "Prob-Dism, Begin of semester"
names(fall2018)[31] <- "Prob-Dism, Most Recent"
names(fall2018)[69] <- "Semester GPA"
names(fall2018)[71] <- "Semester Hrs Failed"
names(fall2018)[72] <- "Semester Hrs Incomplete"
fall2018 <- fall2018[-c(29, 70)]

df1 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Spring 2019, C1-2.xlsx"
  )
df2 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Spring 2019, C3-4.xlsx"
  )
varList <-
  names(df2)[!(names(df2) %in% names(df1))] # get non common names
varList <- c(varList, "EID") # appending key parameter
spring2019 <-
  df1 %>% left_join((df2 %>% select(varList)), by = "EID") %>% mutate(semester = "Spring 2019")
names(spring2019)[4] <- "Academic Status"
names(spring2019)[24] <- "Semester GPA Hrs w/o CBE"
names(spring2019)[30] <- "Prob-Dism, Begin of semester"
names(spring2019)[31] <- "Prob-Dism, Most Recent"
names(spring2019)[69] <- "Semester GPA"
names(spring2019)[71] <- "Semester Hrs Failed"
names(spring2019)[72] <- "Semester Hrs Incomplete"
spring2019 <- spring2019[-c(29, 70)]

df1 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Fall 2019, C1-2.xlsx"
  )
df2 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Fall 2019, C3-4.xlsx"
  )
varList <-
  names(df2)[!(names(df2) %in% names(df1))] # get non common names
varList <- c(varList, "EID") # appending key parameter
fall2019 <-
  df1 %>% left_join((df2 %>% select(varList)), by = "EID") %>% mutate(semester = "Fall 2019")
names(fall2019)[4] <- "Academic Status"
names(fall2019)[24] <- "Semester GPA Hrs w/o CBE"
names(fall2019)[30] <- "Prob-Dism, Begin of semester"
names(fall2019)[31] <- "Prob-Dism, Most Recent"
names(fall2019)[69] <- "Semester GPA"
names(fall2019)[71] <- "Semester Hrs Failed"
names(fall2019)[72] <- "Semester Hrs Incomplete"
fall2019 <- fall2019[-c(29, 70)]

df1 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Spring 2020, C1-2.xlsx"
  )
df2 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Spring 2020, C3-4.xlsx"
  )
varList <-
  names(df2)[!(names(df2) %in% names(df1))] # get non common names
varList <- c(varList, "EID") # appending key parameter
spring2020 <-
  df1 %>% left_join((df2 %>% select(varList)), by = "EID") %>% mutate(semester = "Spring 2020")
names(spring2020)[4] <- "Academic Status"
names(spring2020)[24] <- "Semester GPA Hrs w/o CBE"
names(spring2020)[30] <- "Prob-Dism, Begin of semester"
names(spring2020)[31] <- "Prob-Dism, Most Recent"
names(spring2020)[69] <- "Semester GPA"
names(spring2020)[71] <- "Semester Hrs Failed"
names(spring2020)[72] <- "Semester Hrs Incomplete"
spring2020 <- spring2020[-c(29, 70)]

df1 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Fall 2020, C1-2.xlsx"
  )
df2 <-
  read_excel(
    "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/raw/COLA Toolkit, Fall 2020, C3-4.xlsx"
  )
varList <-
  names(df2)[!(names(df2) %in% names(df1))] # get non common names
varList <- c(varList, "EID") # appending key parameter
fall2020 <-
  df1 %>% left_join((df2 %>% select(varList)), by = "EID") %>% mutate(semester = "Fall 2020")
names(fall2020)[4] <- "Academic Status"
names(fall2020)[24] <- "Semester GPA Hrs w/o CBE"
names(fall2020)[30] <- "Prob-Dism, Begin of semester"
names(fall2020)[31] <- "Prob-Dism, Most Recent"
names(fall2020)[69] <- "Semester GPA"
names(fall2020)[71] <- "Semester Hrs Failed"
names(fall2020)[72] <- "Semester Hrs Incomplete"
fall2020 <- fall2020[-c(29, 70)]


df <-
  rbind(
    spring2016,
    fall2016,
    spring2017,
    fall2017,
    spring2018,
    fall2018,
    spring2019,
    fall2019,
    spring2020,
    fall2020
  )


```

**Cleaning Demographics**

```{r demos}
df2 <- df %>% dplyr::mutate(Ethnicities = replace_na(Ethnicities, "Mixed Race"))

for (i in 1:length(df$Ethnicities)) {
  if (df2$Ethnicities[i] != "White" &
      df2$Ethnicities[i] != "Asian" &
      df2$Ethnicities[i] != "Black or African American" &
      df2$Ethnicities[i] != "Hispanic" &
      df2$Ethnicities[i] != "Native Hawaiian or Other Pacific Islander" &
      df2$Ethnicities[i] != "American Indian or Alaska Native") {
    df2$Ethnicities[i] <- "Mixed Race"
  }
}

```

**Age/High School Rank**

x\$V1 \<- as.numeric(x\$V1)

```{r agehighchoolrank}

df3 <-
  df2 %>% rename(Age = `Current Ageas of today`) %>% mutate_all( ~ gsub(" \\(R\\)| \\*Minor", "", .))

df3$`HS Rank` <- gsub("unknown", "1/1", df3$`HS Rank`)
x <- as.data.frame(str_split_fixed(df3$`HS Rank`, "/", 2))
x$V1 <- as.numeric(x$V1)
x$V2 <- as.numeric(x$V2)
x <- mutate(x, hs_rank = V1/V2 )
df3$hs_rank <- x$hs_rank


```

**Saving**

```{r saving}

write.csv(
  df,
  "C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching/data/processed/cola_totalkit.csv"
)

```
