---
title: "Merging COLA and IPD Data"
output: html_notebook
---

```{r setup}
    knitr::opts_knit$set(root.dir = normalizePath("C:/Users/tenis/Desktop/Data_Projects/UT_Lab-Matching")) 
```

**Libraries**

```{r libraries, message=TRUE, warning=TRUE, include=FALSE}

library(tidyverse)
library(readr)
library(readxl)
library(janitor)
```

**Raw Data**

```{r read_data, message=TRUE, warning=TRUE, include=FALSE}


cola_raw <- read_csv("data/interim/COLA_registrar_total.csv")

ipd_raw <- read_csv("data/raw/Research Affiliates by Year.csv")

```

**Finding EIDs for IPD Students**

-   In order to run any analysis, you need a unique identifier. The data from IPD contains names, but the UT database contains only official full names, which include middles names, and it is very irregular.

```{r getting_eids}

cola <- clean_names(cola_raw)
cola <- select(cola, name, eid, sch_maj1, sch_maj2, email)

#Removing Duplicates
cola <- cola[!duplicated(cola[c(2,5)]),]

ipd <- clean_names(ipd_raw)

#Merging just on email that was provided only for 2020
merged <- left_join(ipd, cola, by = "email")

#Removing middle names if included 
cola$cola_names_filtered <- gsub("\\s*\\w*$", "", cola$name)

#Changing the order of names for joining purposes 
cola$cola_names_filtered <- sub("(\\w+),\\s(\\w+)","\\2 \\1", cola$cola_names_filtered)

merged2 <-left_join(ipd, cola, by = c("name" = "cola_names_filtered"))

```

**IPD Data with Cola ONLY students**

-   This stage involved manually removing students that are not undergraduate in COLA. There were too many of them to do it in a programmatic way, but in subsequent IPD surveys EIDs will be collected

```{r colaonly, message=FALSE, warning=FALSE}
cola <- clean_names(cola_raw)
cola <- select(cola,name, eid, ut_abbr1, sch_maj1, sch_maj2)
cola <- cola[!duplicated(cola[c(2)]),]
#writing csv of COLA database with duplicates of EIDs removed
#write.csv(cola,"data/interim/COLA_duplicates_removed.csv" )

cola$cola_names_filtered <- gsub("\\s*\\w*$", "", cola$name)
cola$cola_names_filtered <- sub("(\\w+),\\s(\\w+)","\\2 \\1", cola$cola_names_filtered)
cola <- cola[,-1]

ipd_cola_only <- read_csv("data/interim/ipd_cola_only.csv")
ipd_cola_only <- ipd_cola_only[1:556,]
ipd_cola_only <- clean_names(ipd_cola_only)

merged3 <- left_join(ipd_cola_only, cola, by = c("name" = "cola_names_filtered"))
merged3 <- select(merged3, name,department_school_major,year, eid)

write.csv(merged3,"data/interim/name_matched_data_missing_some.csv" )

```

**This pulls the eid for those that do not have middle names**

```{r thosethatweremissed, message=FALSE, warning=FALSE}

missed <- merged3
missed_list <- is.na(missed$eid)
missed <- missed[missed_list,]
missed <- missed[,-4]

cola <- clean_names(cola_raw)
cola <- select(cola,name, eid, ut_abbr1, sch_maj1, sch_maj2)
cola <- cola[!duplicated(cola[c(2)]),]
cola$cola_names_filtered <- sub("(\\w+),\\s(\\w+)","\\2 \\1", cola$name)

ipd_cola_only <- read_csv("data/interim/ipd_cola_only.csv")
ipd_cola_only <- ipd_cola_only[1:556,]
ipd_cola_only <- clean_names(ipd_cola_only)

merged4 <- left_join(missed, cola, by = c("name" = "cola_names_filtered"))
merged4 <- select(merged4, name,department_school_major,year, eid)




```

**Even after these last two cells, a significant number still do not have eids**

```{r noeids, message=FALSE, warning=FALSE}

missed2 <- merged4
missed_list2 <- is.na(missed2$eid)
missed2 <- missed2[missed_list2,]
write.csv(missed2,"data/interim/COLA_duplicates_removed_nomatchwithdatabase.csv" )

```

**Merging all of the IPD EID files together after all of the different methods**

```{r grand_merge, message=FALSE, warning=FALSE}



from_1st_match <- !is.na(merged3$eid)
from_1st_match <- merged3[from_1st_match,]
from_2nd_match <- !is.na(merged4$eid)
from_2nd_match <- merged4[from_2nd_match,]
from_3rd_match <-
  read_csv("data/interim/COLA_duplicates_removed_nomatchwithdatabase_eids_assigned.csv")
from_3rd_match2 <- !is.na(from_3rd_match$eid)
from_3rd_match <- from_3rd_match[from_3rd_match2,]

IPD_eid_list <- bind_rows(from_1st_match, from_2nd_match, from_3rd_match)

write.csv(IPD_eid_list,"data/interim/IPD_eid_list_minus2015.csv")

```
